Set working directory

```{r}
dir.create("Project")
setwd("./Project")
```

Load required packages

```{r}
library(data.table)
library(plyr)
```

##1. Merge the training and the test sets to create one data set
####Get the Data 
Step1. Download the file
```{r}
fileUrl<- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
download.file(fileUrl, destfile="./Dataset.zip", mode="wb")
```
Step2. Unzip dataset in a /Project directory and list all files
```{r}
unzip(zipfile="./Dataset.zip")
list.files("UCI HAR Dataset", recursive=TRUE)
```

####Read Activity, Subject and Feature files
First, read Activity, Subject and Features data for Train folder, after that read the same data for Test:
```{r}
get_data<- {setwd("./UCI HAR Dataset/train")
            dActivityTrain<- read.table("./y_train.txt", header=FALSE)
            dSubjectTrain<- read.table("./subject_train.txt", header= FALSE)
            dFeaturesTrain<- read.table("./X_train.txt", header=FALSE)          
            setwd("../")
            setwd("./test")
            dActivityTest <- read.table("./y_test.txt", header=FALSE)
            dSubjectTest <- read.table("./subject_test.txt", header=FALSE)
            dFeaturesTest<- read.table("./X_test.txt", header=FALSE) 
            setwd("../")
            setwd("../")}
```
####Join data tables by rows
```{r}
dSubject<- rbind(dSubjectTrain, dSubjectTest)
dActivity<- rbind(dActivityTrain, dActivityTest)
dFeatures<- rbind(dFeaturesTrain, dFeaturesTest)
```
####Give names to the variables
```{r}
names(dSubject)<- "Subject"
names(dActivity)<- "Activity"

dFeaturesNames <- read.table(("./UCI HAR Dataset/features.txt"),head=FALSE)
head(dFeaturesNames)
names(dFeatures) <- dFeaturesNames$V2 
```
####Merge tables by columns to create one data set (Data) 
```{r}
SubjectActivity<- cbind(dSubject, dActivity)
Data<- cbind(dFeatures, SubjectActivity)
str(Data)
```

##(2) Extract only the measurements on the mean and standard deviation for each measurement

####Subset "Name of Features" by measurements on the mean and standard deviation
```{r}
sdFeaturesNames<-dFeaturesNames$V2[grep("mean\\(\\)|std\\(\\)", dFeaturesNames$V2)]
```
####Subset data set by selected "Names of Features"
```{r}
selectedNames<-c(as.character(sdFeaturesNames), "Subject", "Activity" )
Data<-subset(Data,select=selectedNames)
```

##(3) Use descriptive activity names to name the activities in the data set

####Read activity names and set new column names in the obtained dataset
```{r}
activityNames<- read.table("./UCI HAR Dataset/activity_labels.txt")
names(activityNames)<- c("Activity", "ActivityName")
```
####Factorize the Activity variable 
```{r}
activity<- factor(Data$Activity,
                   levels=c(1:6),
                   labels= activityNames$ActivityName)
Data$Activity<- activity
```
####Check the result
```{r}
head(Data$Activity, 40)
```

##(4) Appropriately label the data set with descriptive variable names

####Check initial names
```{r}
names(Data)
```
####Replace the following:
t -> time
f -> frequency
Acc -> Accelerometer
Gyro -> Gyroscope
Mag -> Magnitude
BodyBody -> Body
std -> SD
mean -> Mean 
```{r}
names(Data)<- gsub("^t", "time", names(Data))
names(Data)<- gsub("^f", "frequency", names(Data))
names(Data)<- gsub("Acc", "Accelerometer", names(Data))
names(Data)<- gsub("Gyro", "Gyroscope", names(Data))
names(Data)<- gsub("Mag", "Magnitude", names(Data))
names(Data)<- gsub("BodyBody", "Body", names(Data))
names(Data)<- gsub("std", "SD", names(Data))
names(Data)<- gsub("mean", "Mean", names(Data))
```
####Check new names
```{r}
names(Data)
```

## (5) Create a second, independent tidy data set with the average of each variable for each activity and each subject
```{r}
Data2<-aggregate(. ~Subject + Activity, Data, mean) 
Data2
```
This data set a is set of variables for each activity and subject. As there are 30 subjects and 6 ativities, initial 10299 observations were split into 180 groups. The data set provides average mean and standard deviation features for each group. 
